\iffalse
\title{2021}
\author{ee24btech11009}
\section{integer}
\fi
%\begin{enumerate}
\item Let $\lfloor t\rfloor$ denote the greatest integer $\leq t$. Then the value of $8 \cdot \int_{\frac{-1}{2}}^{1} \brak{\lfloor 2x\rfloor + \abs{x}} dx $
is.\hfill{[Aug 2021]}
\item A point $z$ moves in the complex plane such that 
$\arg\brak{\frac{z - 2}{z + 2}} = \frac{\pi}{4}$, then the minimum value of $\abs{z - 9\sqrt{2} - 2i}^2$ is equal to.\hfill{[Aug 2021]}
\item  The square of the distance of the point of intersection of the line 
$\frac{x - 1}{2} = \frac{y - 2}{3} = \frac{z - 1}{6}$
and the plane $2x - y + z = 6$ from the point $\brak{-1, -1, 2}$ is.\hfill{[Aug 2021]}
\item If $R$ is the least value of $a$ such that the function $f(x) = x^2 + ax + 1$ is increasing on $\sbrak{1, 2}$ and $'S'$ is the greatest value of $'a'$ such that the function $f(x) = x^2 + ax + 1$ is decreasing on $\sbrak{1, 2}$, then the value of $\abs{R - S}$ is.\hfill{[Aug 2021]}
\item The mean of 10 numbers $7 \times 8, 10 \times 10, 13 \times 12, 16 \times 14, \dots$ is.\hfill{[Aug 2021]}
\item  If the variable line $3x + 4y = \alpha$ lies between the two circles $\brak{x - 1}^2 + \brak{y - 1}^2 = 1$ and $\brak{x - 9}^2 + \brak{y - 1}^2 = 4$, without intercepting a chord on either circle, then the sum of all the integral values of $\alpha$ is.\hfill{[Aug 2021]}
\item The number of six letter words (with or without meaning), formed using all the letters of the word 'VOWELS', such that all the consonants never come together, is.\hfill{[Aug 2021]}
\item If $x\phi\brak{x} =\int_{5}^{x}\left(3t^2 - 2\phi^\prime\brak{t}\right) dt, x > -2$
and $\phi\brak{0} = 4$, then $\phi\brak{2}$ is.\hfill{[Aug 2021]}
\item If $\brak{\frac{3^6}{3^4}}k \text{ is the term independent of } x$, in the binomial expansion of $\brak{\frac{x}{4} - \frac{12}{x^2}}^{12}
$ then $k$ is.\hfill{[Aug 2021]}
\item An electric instrument consists of two units. Each unit must function independently for the instrument to operate. The probability that the first unit functions is $0.9$ and that of the second unit is $0.8$. The instrument is switched on and it fails to operate. If the probability that only the first unit failed and the second unit is functioning is $p$, then $98p$ is equal to.\hfill{[Aug 2021]}
%\end{enumerate}
