\iffalse
\title{2021}
\author{AI24BTECH11008}
\section{integer}
\fi
     \item Let $ P $ be a plane containing the line 
$\frac{x - 1}{3} = \frac{y + 6}{4} = \frac{z + 5}{2}$
and parallel to the line $\frac{x - 3}{4} = \frac{y - 2}{-3} = \frac{z + 5}{7}.$ If the point $\brak{1, -1, \alpha}$ lies on the plane $P$, then the value of $\brak{\abs{5\alpha}}$ is equal to?\hfill{[March 2021]}
     \item $ \sum_{r=1}^{10} r! \brak{r^3 + 6r^2 + 2r + 5} = \alpha\brak{11!}$
Then the value of $\alpha$ is equal to:\hfill [March 2021]
     \item The term independent of $x$ in the expansion of$\brak{\frac{x + 1}{x^{2/3} - x^{1/3} + 1} - \frac{x - 1}{x - x^{1/2}}}^{10}, \quad x \neq 1$ is equal to?\hfill [March 2021]
     \item  Let $^nC_r$ denote the binomial coefficient of $x^r$ in the expansion of $\brak{1 + x}^n$. If $\sum_{k=0}^{10} \brak{22 + 3k}   ^nC_k = \alpha \cdot 3^{10} + \beta \cdot 2^{10},$then $\alpha + \beta$ is equal to?\hfill [March 2021]
      \item Let $P\brak{x}$ be a real polynomial of degree 3 which vanishes at $x = -3$. Let $P\brak{x}$ have local minima at $x = 1$, local maxima at $x = -1$, and $\int_{-1}^{1} P(x) dx = 18,$then the sum of all the coefficients of the polynomial $P\brak{x}$ is equal to?\\\hfill [March 2021]
     \item Let the mirror image of the point \brak{1, 3, a} with respect to the plane $\mathbf{r} \cdot \brak{2\mathbf{i} - \mathbf{j} + \mathbf{k}} - b = 0$ be \brak{-3, 5, 2}, Then, the value of $\abs{a + b}$ is equal to?\hfill [March 2021]
     \item If $f\brak{x}$ and $g{x}$ are two polynomials such that the polynomial $P\brak{x} = f\brak{x^3} + x g\brak{x^3}$ is divisible by $x^2 + x + 1$, then $P\brak{1}$ is equal to?\hfill [March 2021]
     \item Let I be an identity matrix of order $2 \times 2$ and 
$$P=\begin{bmatrix}
    2 & -1\\
    5 & -3
 \end{bmatrix}$$ 
$P_n = 5I - 8P$ Then the value of $n \in \mathbb{N}$ for which $P_n = 5I - 8P$ is equal to?\hfill [March 2021]
    \item Let $f : \mathbb{R} \to \mathbb{R}$ satisfy the equation$f\brak{x + y} = f\brak{x} \cdot f\brak{y}$ for all $x, y \in \mathbb{R}$ and $f\brak{x} \neq 0$ for any $x \in \mathbb{R}$. If the function $f$ is differentiable at $x = 0$ and $f'\brak{0} = 3$, then $\lim_{h \to 0} \frac{1}{h} [f(h) - 1] $
is equal to?\hfill [March 2021]
    \item Let $y = y\brak{x}$ be the solution of the differential equation 
$x dy - y dx = \sqrt{x^2 - y^2} \, dx, \quad x \geq 1,$ with $y\brak{1} = 0$. If the area bounded by the line $x = 1$, $x = e^\pi$, $y = 0$ and $y = y\brak{x}$ is $\alpha e^{2\pi} + \beta, $then the value of $10 \brak{\alpha + \beta}$ is equal to?\hfill [March 2021]

