\iffalse
\title{04-04-2024}
\author{AI24BTECH11032}
\section{integer}
\fi

\item If $\lim_{x \to 1} \frac{\brak{5x+1}^{\frac{1}{3}}-\brak{x+5}^{\frac{1}{3}}}{\brak{2x+3}^{\frac{1}{2}}-\brak{x+4}^{\frac{1}{2}}}=\frac{m\sqrt{5}}{n\brak{2n}^\frac{2}{3}},$ where $gcd\brak{m,n}=1,$ then $8m+12n$ is equal to.\hfill{April-2024}
\item In a survey of $220$ students of a higher secondary
school, it was found that at least $125$ and at most
$130$ students studied Mathematics; at least $85$ and
at most $95$ studied Physics; at least $75$ and at most
$90$ studied Chemistry; $30$ studied both Physics and
Chemistry; $50$ studied both Chemistry and
Mathematics; $40$ studied both Mathematics and
Physics and $10$ studied none of these subjects. Let
m and n respectively be the least and the most
number of students who studied all the three
subjects. Then $m + n$ is equal to\hfill{April-2024}
\item Let the solution $y=y\brak{x}$ of the differential equation $\frac{dy}{dx}-y=1+4sinx$ satisfy $y\brak{\pi}=1.$ Then $y\brak{\frac{\pi}{2}+10}$ is equal to.\hfill{April-2024}
\item If the shortest distance between the lines $\frac{x+2}{2}=\frac{y+3}{3}=\frac{z-5}{4}$ and $\frac{x-3}{1}=\frac{y-2}{-3}=\frac{z+4}{2}$ is $\frac{38}{3\sqrt{5}}k$ and $\int_{0}^{k}\sbrak{x^{2}}dx=\alpha-\sqrt{\alpha
},$ where $\sbrak{x}$ denotes the greatest integer function, then $6\alpha^{3}$ is equal to.\hfill{April-2024}
\item Let A be a square matrix of order 2 such that $\abs{A}=2$
and the sum of its diagonal elements is $-3.$ If the point$\brak{x,y}$ satisfying $A^{2}+xA+yI=0$ lie
on a hyperbola, whose transverse axis is parallel to
the x-axis, eccentricity is e and the length of the
latus rectum is l,then $e^{4}+l^{4}$ is equal to.\hfill{April-2024}
\item let $a=1+\frac{^2C_2}{3!}+\frac{^3C_2}{4!}+\frac{^4C_2}{5!}+\cdots,$
$b=1+\frac{^1C_0+^1C_1}{1!}+\frac{^2C_0+^2C_1+^2C_2}{2!}+\frac{^3C_0+^3C_1+^3C_2+^3C_3}{3!}+\cdots$ Then $\frac{2b}{a^{2}}$ is equal to .\hfill{April-2024}
\item Let A be a $3\times3$ matrix of non-negative real
elements such that $A \cdot \begin{bmatrix} 1 \\ 1 \\ 1 \end{bmatrix} = 3 \cdot \begin{bmatrix} 1 \\ 1 \end{bmatrix}
$ Then the maximum value of $det\brak{A}$ is.\hfill{April-2024}
\item Let the length of the focal chord PQ of the
parabola $y^{2} = 12x$ be 15 units. If the distance of PQ
from the origin is p, then $10p^{2}$ is equal to.\hfill{April-2024}
\item Let ABC be a triangle of area $15\sqrt{2}$ and the vectors $\overrightarrow{AB}=\hat{i}+2\hat{j}-7\hat{k},$ $\overrightarrow{BC}=a\hat{i}+b\hat{j}+c\hat{k}$ and $\overrightarrow{AC}=6\hat{i}+d\hat{j}-2\hat{k},$ $d>0.$ Then The square of the length of the largest side of the triangle ABC is .\hfill{April-2024}
\item If $\int_{0}^{\frac{\pi}{4}}\frac{\sin^{2}{x}}{1+\sin{x}\cos{x}}dx=\frac{1}{a}\log_{e}\brak{\frac{a}{3}}+\frac{\pi}{b\sqrt{3}},$ where $a,b\in N ,$ then $a+b$ is equal to. \hfill{April-2024}
